### 2019-05-24 5_evaluation.tex
Trim some text.

Our MPI+CUDA implementation uses an offload model in which input and
output data is copied to and from the GPU on each time step. We tested
two configurations: \lstinline{w1} uses 1 task per GPU, whereas
\lstinline{w4} overdecomposes by a factor of $4\times$, using 4 MPI
ranks per GPU to push work to the GPU in parallel and thus achieve
some overlap between communication and computation. We see that the
overdecomposed \lstinline{w4} configuration achieves higher FLOP/s but
drops more rapidly at smaller problem sizes, due to the overhead of
scheduling $4\times$ as many CUDA kernel launches. In either case, the
GPU requires more work to achieve high performance, and the overhead
of copying data to and from the GPU dominates at small task
granularities. Thus at smaller problem sizes the CPU achieves higher
performance. While Figure~\ref{fig:cuda-efficiency} is not couched in
terms of MTEG (as the peak performance of the GPU and CPU are very
different), the conclusion here is similar to
Section~\ref{subsec:scalability}: The cost of communicating data and
tasks to and from the GPU imposes a higher task granularity to achieve
the same efficiency than running on the CPU, reducing the advantage of
MPI's very lightweight mechanisms.

>>>>

Our MPI+CUDA implementation uses an offload model in which input and
output data is copied to and from the GPU on each time step. We tested
two configurations: \lstinline{w1} uses 1 task per GPU, whereas
\lstinline{w4} overdecomposes by a factor of $4\times$, using 4 MPI
ranks per GPU to push work to the GPU in parallel and thus overlaps communication and computation. We see that the
\lstinline{w4} configuration achieves higher FLOP/s but
drops more rapidly at smaller problem sizes, due to the overhead of
scheduling $4\times$ as many CUDA kernel launches. In either case, the
GPU requires more work to achieve high performance, and the overhead
of copying data to and from the GPU dominates at small task
granularities. Thus at smaller problem sizes the CPU achieves higher
performance. While Figure~\ref{fig:cuda-efficiency} is not couched in
terms of MTEG (as the peak performance of the GPU and CPU are very
different), the conclusion here is similar to
Section~\ref{subsec:scalability}: The cost of communicating data and
tasks to and from the GPU imposes a higher task granularity to achieve
the same efficiency than running on the CPU, reducing the advantage of
MPI's very lightweight mechanisms.
